---
title: "UCT Kenya Dashboards"
author: "Rafael Charris"
date: "11/22/2021"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
runtime: shiny
---

```{r setup, include=FALSE, message=FALSE, warning=FALSE}
library(flexdashboard)
library(knitr)
library(haven) # to read dta files
library(foreign)
library(leaflet)
library(tidyverse)
library(osmdata)
library(htmltools) # tools for the map
library(sf)
library(ggmap)
library(shinyWidgets)
library(plotly)
library(ggthemes)
library(dagitty)

theme_set(theme_minimal())
#General data set
df <- read.dta("./data/cashtransfers_v12.dta") %>%
  filter

#load price data
df_price <- readxl::read_xls("./data/villages.xls")
# Merge both data sets by village
df_merge <- df %>%
  left_join(df_price, by = "village")
# for the price analysis
price_plot <- df_merge %>% 
  group_by(village) %>%
  mutate(transaction = ifelse(treat == 1 | spillover == 1, 1, 0)) %>%
  distinct(village, .keep_all = TRUE) %>%
  select(village, sublocation, longitude, latitude, v_price_index, purecontrol, transaction)

price_plot_summary <- price_plot %>%
  group_by(purecontrol) %>%
  summarise(mean_price = mean(v_price_index),
            sd_price = sd(v_price_index))

df_plot = df %>%
  filter(!is.na(gender), !is.na(wvs_happiness))
#kenya_geo <- sf::st_read("data/kemajor-towns/ke_major-towns.shp")
```

General Presentation
==================

Row 
-----------------------------------------------------------------------

### Purpose of the project

This program was implemented by the NGO **Give Directly** between 2011 and 2013 in western Kenya. The purpose of this NGO is to make unconditional cash transfers to poor households in developing countries. The evaluation of this program was conducted by a team of researchers from Princeton and Busara Center of Behavioral Economics led by Johannes Haushofer and Jeremy Shapiro.

#### Design

#### Double randomization

```{r}
renderImage({
    list(src = "design.png", wight = 200, height = 170)
  }, deleteFile = FALSE)
```

1. Selection criteria for villages: Highest proportion of thatched roofs.
2. Monthly Transfer. Total: 25.200 KES (404 USD PPP)
3. 9\% of the households choosen
<!--
1. amount given
2. How did they select the villages (120 villages with the highest proportion of tatched roofs)
3. All elegible villages were identified with a census
3. approx 19 percent of the households within each village where surveyed, and approx 9 percent of the households within a village got a transfer
4. Population of villages ?
5. amount of transfer 25.200 KES (404 USD PPP)
13,471 KES was the minimum wage in 2012
1 usd = 62.4 KES
-->
4. Potential Problem: purecontrol villages were identified 1 year later than their treatment villages controls counterparts

#### Description of the variables

* `price index`: Aggregated and normalized index of prices at endline.
* `Happiness`: World Values Survey responses
* `Life Satisfaction`: World Values Survey responses
* `Consumption` vars: Level of consumption the past week (KES)

### Research Questions

1. Does the UCT program increase the prices in the treated villages relative to the pure control villages?

2. Does receiving money increase social consumption of households?

3. Does receiving money increase food consumption of households?

4. Does receiving money increase happiness and/or life satisfaction?

5. Are there any gender effects on consumption?

Village Level
==================

Row 
-----------------------------------------------------------------------
### Description
Each point is a village in which the study was conducted.
The plot on the left shows the distribution of the price indices.

Row
-----------------------------------------------------------------------

### Price Distribution
```{r}
p <- ggplot(price_plot, 
            aes(x = as.factor(purecontrol), 
                y = v_price_index
            )) +
  geom_jitter(
    #position = "jitter",
    aes(text = paste0(village, "\nPrice Index: ", round(v_price_index,2))),
    width = 0.25
  ) + 
  stat_summary(fun = mean,
               col = "red",
               geom = "point") +
  labs(y = "Price Index", x = "Treated Village") 

renderPlotly({
  ggplotly(p, tooltip = "text")
    })
```

### Rarieda´s Map 
```{r message=FALSE, warning=FALSE}
pal <- colorNumeric(
  palette  = c("green3", "red"), 
  domain = df$purecontrol)

 output$kenyamap <- renderLeaflet({
  price_plot%>%
  #distinct(village, .keep_all = TRUE) %>%
  leaflet() %>%
  addTiles() %>%
  addCircles(label = ~htmlEscape(village),
             color = ~pal(transaction)) %>%
  addLegend(
    title = "Received Transaction",
    label = c("Yes", "No"),
            color = ~pal(unique(transaction)))
   })
leafletOutput("kenyamap")
```

Household Level Analysis
==================

Inputs {.sidebar}
-----------------------------------------------------------------------

```{r}
radioButtons("effectInput", label = h3("Effect"), 
                   choices =  c("Transaction effect", "Spillover Effect"),
                   selected = "Transaction effect")
#pickerInput("villageInput", label = h3("Village"), 
# choices = sort(unique(levels(df_plot$village))),
# selected = sort(unique(levels(df_plot$village))),
#   multiple = TRUE,
#  options = list(
#        `actions-box` = TRUE,
#        size = 10,
#        `selected-text-format` = "count > 3"
#      ),)
```


Row{.tabset}
-----------------------------------------------------------------------
### Happiness
```{r}
well_being_plot <- reactive(
  if (input$effectInput == "Transaction effect"){
    df_plot %>%
      filter(treat == 1 | purecontrol == 1) %>%
      ggplot(aes(x = as.factor(wvs_happiness),
                 y = ..count../sum(..count..),
                 fill = as.factor(treat))) +  
       geom_histogram(
         stat = "count",
        position = "dodge",
        alpha = 0.5,
        col = "black"
         ) +
      labs(y = "Wellbeing", x = "Happines Level",
           title = "Effect of Receving a Transaction",
           fill = "Treatment") + 
      scale_y_continuous(labels = function(x)paste0(x*100, "%"))
                          
  } else{
    df_plot %>%
      filter(treat == 0 | purecontrol == 1) %>%
      ggplot(aes(x = wvs_happiness,
                 y = ..count../sum(..count..),
                 fill = as.factor(spillover))) +  
      geom_histogram(stat = "count", 
                     position = "dodge",
                       alpha = 0.5,
        col = "black") +
      labs(y = "Wellbeing", x = "Hoseholds in Treated village",
           title = "Spillover Effect",
           subtitle = "Households that did not received a transaction in treated villages vs households that did not received a transaction in non-treated villages.",
           fill = "Spillover")  + 
      scale_y_continuous(labels = function(x)paste0(x*100, "%"))
  }
  
)
renderPlot({
  well_being_plot() 
})
```


### Life-Satisfaction
```{r}
life_satisfaction_plot <- reactive(
  if (input$effectInput == "Transaction effect"){
    df_plot %>%
      filter(treat == 1 | purecontrol == 1) %>%
      ggplot(aes(x = as.factor(wvs_life_sat), 
                   y = ..count../sum(..count..),
                 fill = as.factor(treat))
             ) +  
      geom_histogram(stat = "count", 
                    position = position_dodge(width = 0.7),
                           alpha = 0.5,
        col = "black") +
      labs(y = "Wellbeing", x = "Life Satisfaction",
           title = "Effect of Receving a Transaction in Life Satisfaction",
           fill = "Treated")  + 
      scale_y_continuous(labels = function(x)paste0(x*100, "%")) 
                          
  } else{
      df_plot %>%
      filter(treat == 0 | purecontrol == 1) %>%
      ggplot(aes(x = as.factor(wvs_life_sat), 
                   y = ..count../sum(..count..),
                 fill = as.factor(spillover))) +  
      geom_histogram(stat = "count", 
                     position = position_dodge(width = 0.7),
                           alpha = 0.5,
        col = "black") +
      labs(y = "Wellbeing", x = "Life Satistifaction",
           title = "Spillover Effect",
           subtitle = "Households that did not received a transaction in treated villages vs households that did not received a transaction in non-treated villages.",
           fill = "Spillover")  + 
      scale_y_continuous(labels = function(x)paste0(x*100, "%")) 
  }
)
renderPlot({
  life_satisfaction_plot() 
})
```


### Social Consumption

```{r}
filtered_1 <- reactive({
  if (input$effectInput == "Transaction effect"){
    df_plot %>%
      filter(treat == 1 | purecontrol == 1) %>%
      ggplot(aes(x = cons_social,
                 fill = as.factor(treat))) +
      geom_density(alpha = 0.5) + 
      labs(y = "Density", 
           x = "KES",
           title = "Effect of Receving a Transaction on Social Consumption",
           fill = "Treatment")
  } else {
    df %>% 
      filter(purecontrol == 1 | treat ==0) %>%
      ggplot(aes(x = cons_social,
               fill = as.factor(spillover))) +
  geom_density(alpha = 0.5) + 
     labs(x = "KES", y = "Density", 
          fill = "Spillover",
           title = "Spillover Effect")
  }
})

renderPlot({
  filtered_1() 
})
```

### Cumulative Distribution SC
```{r}
renderPlot({
  if (input$effectInput == "Transaction effect"){
    df_plot %>%
      filter(treat == 1 | purecontrol == 1) %>%
      ggplot(aes(x = cons_social,
                 col = as.factor(treat))) +
      stat_ecdf()+
      labs(x = "KES", y = "ECDF", 
           col = "Treatment",
           title = "Cumulative Distribution function for food consumption",
           subtitle = paste0("p = ",
                             round(ks.test(
                               df_plot$cons_social[df_plot$treat == 1],
                               df_plot$cons_social[df_plot$treat == 0 &
                               df_plot$purecontrol==1])$p.value,3))) 
  } else {
    df_plot %>%
      filter(purecontrol == 1 | treat == 0) %>%
      ggplot(aes(x = cons_social,
                 col = as.factor(spillover))) +
      stat_ecdf()+
      labs(x = "KES",
           y = "ECDF",
           col = "Spillover",
           title = "Cumulative Distribution function for food consumption",
           subtitle = paste0("p = ",
                             round(ks.test(
                               df_plot$cons_social[df_plot$purecontrol == 0 & df_plot$treat == 0],
                               df_plot$cons_social[df_plot$purecontrol == 1])$p.value,3)))
  }
  
})
```

### Food Consumption
```{r}
filtered_2 <- reactive({
  if (input$effectInput == "Transaction effect"){
    df_plot %>%
      ggplot(aes(x = cons_food, fill = as.factor(treat))) +
      geom_density(alpha = 0.5) + 
      labs(x = "KES",
           y = "Density",
           fill = "Treatment",
           title = "Effect of Receving a Transaction on Food Consumption"
)
    }
  else {
    df_plot %>%
      filter(treat == 1 | purecontrol == 0) %>%
      ggplot(aes(x = cons_food,
                 fill = as.factor(spillover))) +
       geom_density(alpha = 0.5) + 
      labs(x = "KES",
           y = "Density",
           fill = "Spillover",
                      title = "Spillover effect on Food Consumption"
) 
    }
})
renderPlot({
filtered_2() 
})
```

### Cumulative Distribution FC
```{r}
renderPlot({
  if (input$effectInput == "Transaction effect"){
    df_plot %>%
      filter(treat == 1 | purecontrol == 1) %>%
      ggplot(aes(x = cons_food,
                 col = as.factor(treat))) +
      stat_ecdf()+
      labs(x = "KES", y = "ECDF", 
           col = "Treatment",
           title = "Cumulative Distribution function for food consumption",
           subtitle = paste0("p = ",
                             round(ks.test(
                               df_plot$cons_food[df_plot$treat == 1],
                               df_plot$cons_food[df_plot$treat == 0 &
                               df_plot$purecontrol==1])$p.value,3))) 
  } else {
    df_plot %>%
      filter(treat == 0 | purecontrol == 0) %>%
      ggplot(aes(x = cons_food,
                 col = as.factor(spillover))) +
      stat_ecdf()+
      labs(x = "KES",
           y = "ECDF",
           col = "Spillover",
           title = "Cumulative Distribution function for food consumption",
           subtitle = paste0("p = ",
                             round(ks.test(
                               df_plot$cons_food[df_plot$purecontrol == 0 & df_plot$treat == 0],
                               df_plot$cons_food[df_plot$purecontrol == 1])$p.value,3)))
  }
  
})
```


Statistical Analysis
==================

Row {.tabset}
-----------------------------------------------------------------------
### Happiness

#### Ordinal Multilevel Logit Model

1. I will run to of these regressions one for the effect of the treatment, one for the spillover effect.

2. My dependent variable is a discrete ordered variable $y \in \{1,2,3,4,5\}$

3. My regression should show me the difference in well being depdening on gender

4. The regression should tell me the probability of going from 1 level of happiness to the next.


### Consumption Variables
#### Multilevel Model
1. I need a multilevel model here that let's me estimate the effect of the treatment on the different measures of consumption.

2. I assume that there are different intercepts per village.

3. I want to explore if there are gender effects on the consumption practices of people.
```{r, echo = FALSE, fig.dim = c(3,4), fig.cap = "DAG for question 1", eval = FALSE}
dag_q1 <- dagitty(
  "dag{
  Treatment -> Consumption
  Gender -> Consumption
  NumKids -> Consumption
  HouseholdSize -> Consumption
  Education -> Consumption
  }"
)
plot(dag_q1)
```
$$\text{Consumption} \sim \text{Log-Normal}(\mu, \sigma)$$
$$\mu \sim  \beta_{1[treat]} + \beta_{2[female]} + \beta_{3[treatXfemale]} + \beta_{4[village]}$$
$$\beta_{1[treat]} \sim \text{Log-Normal}(4000, 1000)$$
$$\beta_{2[female]} \sim \text{Log-Normal}(4000, 1000)$$
$$\beta_{3[treatXfemale]} \sim \text{Log-Normal}(4000, 1000)$$
$$\beta_{4[village]} \sim \text{Log-Normal}(\bar{\alpha}, \tau)$$
$$\bar{\alpha} \sim \text{Log-Normal}(2000, 500)$$
$$\sigma \sim \text{Exponential}(0.001);\tau \sim \text{Exponential}(0.001)$$

Final
==================

### To-do
* Take care of missing values and outliers
* Run the multilevel regressions for the household level variables
* Run the ordinal regressions
* Explore gender effects on consupmtion and happiness


### Limitations
* The pure control group was choosen at the endline
* Spending practices are not exhausted by food, and social consuption. Ex: savings, alcohol
* I don't have information on the population of each village
* Spillover effect among villages?
