---
title: "UBI Kenya Dashboards"
author: "Rafael Charris"
date: "11/22/2021"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    source_code: embed
runtime: shiny
---

```{r setup, include=FALSE, message=FALSE, warning=FALSE}
library(flexdashboard)
library(haven) # to read dta files
library(foreign)
library(leaflet)
library(tidyverse)
library(osmdata)
library(htmltools) # tools for the map
library(sf)
library(ggmap)
library(shinyWidgets)
library(plotly)
library(ggthemes)

#General data set
df <- read.dta("./data/cashtransfers_v12.dta") %>%
  filter

#load price data
df_price <- readxl::read_xls("./data/villages.xls")
# Merge both data sets by village
df_merge <- df %>%
  left_join(df_price, by = "village")
# for the price analysis
price_plot <- df_merge %>% 
  group_by(village) %>%
  mutate(transaction = ifelse(treat == 1 | spillover == 1, 1, 0)) %>%
  distinct(village, .keep_all = TRUE) %>%
  select(village, sublocation, longitude, latitude, v_price_index, purecontrol, transaction)

price_plot_summary <- price_plot %>%
  group_by(purecontrol) %>%
  summarise(mean_price = mean(v_price_index),
            sd_price = sd(v_price_index))

df_plot = df %>%
  mutate(treat = ifelse(treat == 1, "UCT == Yes", "UCT == No"))
#kenya_geo <- sf::st_read("data/kemajor-towns/ke_major-towns.shp")
```

General Presentation
==================

Row 
-----------------------------------------------------------------------

### Purpose of the project

Here I explain what the project consists on 

#### Design

This program was implemented by the NGO **Give Directly** between 2011 and 2013 in western Kenya. The purpose of this NGO is to make unconditional cash transfers to poor households in developing countries. The evaluation of this program was conducted by a team of researchers from Princeton and Busara Center of Behavioral Economics led by Johannes Haushofer and Jeremy Shapiro.

The design has two levels of randomization and three treatments. The first level of 
Households were selected if they had thatched roof[^1]. They choose the household using a survey.
[1 I don't know if this is a good criteria for deciding which household was the poorest]
After identification, representatives of GD went to each elected household and told the recipient that they would received 404 USD total. They were informed also about the schedule of the transaction (lump-sum vs direct).
They were given a SIM card and were asked to register to the service M-Pesa: a mobile banking service present in Kenya, Tanzania, Afganistan, Uganda, Rwanda and Tanzania.


1. amount given
2. How did they select the villages (120 villages with the highest proportion of tatched roofs)
3. All elegible villages were identified with a census
3. approx 19 percent of the households within each village where surveyed, and approx 9 percent of the households within a village got a transfer
4. Population of villages ?
5. amount of transfer 25.200 KES (404 USD PPP)
13,471 KES was the minimum wage in 2012
1 usd = 62.4 KES

questions: 
1. frequency of the transfers 
2. baseline and results dates

Problem: purecontrol villages were identified 1 year later than their treatment villages controls counterparts

map -> what color is non treated and what color is treated

#### Description of the variables

* `price index`: 
* `well being`: aggregated

### TO-DO

* Take care of missing values

Dashboard
==================

Inputs {.sidebar}
-----------------------------------------------------------------------

```{r}
pickerInput("villageInput", label = h3("Village"), 
 choices = sort(unique(levels(df_plot$village))),
 selected = sort(unique(levels(df_plot$village))),
   multiple = TRUE,
  options = list(
        `actions-box` = TRUE,
        size = 10,
        `selected-text-format` = "count > 3"
      ),)

checkboxGroupInput("treatmentInput", label = h3("Treatment"), 
                   choices = unique(df_plot$treat),
                   selected = unique(df_plot$treat))
checkboxGroupInput("purecontrolInput", label = h3("Pure Control"), 
                   choices = unique(df_plot$purecontrol),
                   selected = 0)
checkboxGroupInput("genderInput", label = h3("Gender"), 
                   choices = unique(df_plot$gender),
                   selected = unique(df_plot$gender))

```

### Description

Each point is a village in which the study was conducted. Feel free to change which villages you want to see. You can see how the UCT affected the region or how it affected the households within each village

Row {data-height=300}
-----------------------------------------------------------------------

### Kenya´s Map 

```{r message=FALSE, warning=FALSE}
pal <- colorNumeric(
  palette  = c("blue", "red"), 
  domain = df$purecontrol)

 output$kenyamap <- renderLeaflet({df %>%
  distinct(village, .keep_all = TRUE) %>%
  leaflet() %>%
  addTiles() %>%
  addCircles(label = ~htmlEscape(village),
             color = ~pal(purecontrol))})
leafletOutput("kenyamap")
```

Row {.tabset}
-----------------------------------------------------------------------

### Price Distributions
```{r}
renderText({
 
})


p <- ggplot(price_plot, 
       aes(x = as.factor(purecontrol), 
           y = v_price_index
           )) +
    geom_jitter(
      #position = "jitter",
             aes(text = paste0(village, "\nPI: ", round(v_price_index,2))),
             width = 0.25
             ) + 
  stat_summary(fun = mean,
             col = "red",
             geom = "point") +
  labs(y = "Price Index", x = "Treated Village") +
  theme_minimal()

renderPlotly({ggplotly(p, tooltip = "text")
    })
```


### Well-Being
```{r}
filtered <- reactive(df_plot %>%
                       filter(
                              treat %in%input$treatmentInput,
                              purecontrol %in% input$purecontrolInput,
                              gender %in% input$genderInput)
)
renderPlot({
  filtered() %>%
    ggplot(aes(x = as.factor(treat), y = wvs_happiness)) +  
    geom_point( position = "jitter") +
    labs(y = "Wellbeing", x = "Treatment") 
  #+   theme_wsj()
})
```


### Social Consumption
```{r}
filtered_1 <- reactive({
  df_plot %>% 
    filter(treat %in% input$treatmentInput,
           purecontrol %in% input$purecontrolInput,
           gender %in% input$genderInput) 
})
renderPlot({
  filtered_1() %>%
    ggplot(aes(x = cons_social,
              # y = ..prop..,
               fill = as.factor(treat))) +
    geom_density(alpha = 0.5) + 
    #geom_bar(
      #position = 'dodge', This is for the graphs to be completely separated 
     # position = position_dodge(width = 0.7),
      #col = 'black') +
    #theme_wsj() +
    labs(x = "$", y = "Density", fill = "Treatment")

})

renderPlot({
  df %>% 
    filter(purecontrol == 1 | treat ==1) %>%
    group_by(female) %>%
    #mutate(per = n()/nrow(df)) %>%
    #ungroup() %>%
    ggplot(aes(x = cons_social,
               y = per,
               fill = as.factor(treat))) +
    geom_histogram(alpha = 0.5,
                   position = "dodge",
                   bins = 10
                   ) + 
    facet_wrap(.~female) +
     labs(x = "$", y = "Percentage", fill = "Treatment") + 
    scale_y_continuous(labels = function(x)paste0(x*100,"%"))
})
```

### Food Consumption
```{r}
filtered_1 <- reactive({
  df_plot %>% 
  filter(treat %in% input$treatmentInput,
         purecontrol %in% input$purecontrolInput,
         gender %in% input$genderInput) 
})
renderPlot({
filtered_1() %>%
  ggplot(aes(x = cons_food, fill = as.factor(treat))) +
  geom_density(alpha = 0.5) + 
  labs(x = "$", y = "Density")
})
```

Statistical Analysis
==================

Row {.tabset}
-----------------------------------------------------------------------

### KS Food Consumption

```{r}
renderPlot({
  filtered_1() %>%
    ggplot(aes(x = cons_food,
               col = as.factor(treat))) +
    stat_ecdf()+
    labs(x = "$", y = "ECDF", fill = "Treatment")
})
```

### KS social Consumption
```{r}
renderPlot({
  df %>%
    filter(purecontrol == 1 | treat ==1) %>%
    ggplot(aes(x = cons_social,
               col = as.factor(treat))) +
    stat_ecdf() +
    labs(x = "$", y = "ECDF", fill = "Treatment")
})
```

